Imm algorithm implementation for tracking

### 2020-01-30 Latex/exp.tex
sssss

\section*{Introduction}
\justify
The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
agent's traking. The agent switches between linked models of movement by the means of a Markov chain. The goal is evaluate the best trade-off
between error on estimated position and real position and number of messagesses involved in the tracking.

@@

    The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep and

@@

    between one sensor and the following one in any direction in the grid, as soon as the agent exceed the range the device will stop sensing.

@@

    more power efficient and to avoid useless data stream towards sensors that aren't currently in range.

@@

    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure before.

@@

    The set of active sensors is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 

@@

    The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
    sensors turned on depends on working range choosed and position of target. The mechanism that regulate the transition from sensors state
    relay on the information exchanged with nearby sensor. Different state can receive and send different messagesses. A sensor in On state has the moving

@@

        z(k)=H(k)x(k)+\textbf{R}

@@

@@

            dopo & la \\
            scr  & vo \\

@@

    \subsection*{Random walk and Unycicle model}
    The target in this simulation can move accordingly to two families of models, both are Markov processes.
    \\
    TABELLA CON DA UNA PARTE LE MODES DI UNO E DELL'ALTRO AL POSTO DI SPIEGARLO A PAROLE
    \\
    Each of this model has a Markov chain that
    regulate how the given input goes in the system. For the random walk we have 5 state: costant velocity, positive or negative acceleration
    on x direction and positive or negative deceleration on y direction. So the input are $\ddot{x}$ and $\ddot{y}$. The Transition matrix 
    associated with the Markov's chain is shown below
    $$\begin{vmatrix}
            0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
        \end{vmatrix}$$
    The linear system describing the evolution of the state is 
    \begin{equation}
        X^{+}= \textbf{A}X(k) + \textbf{B}u(k) + \textbf{G}w(k)
    \end{equation}
    State,state and noise matrix associate to the random walk has shown below:
    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
            1 & 0 & \delta & 0      \\
            0 & 1 & 0      & \delta \\
            0 & 0 & 1      & 0      \\
            0 & 0 & 0      & 1      \\
        \end{bmatrix}
        G=\begin{bmatrix}
            \delta^2/2 & 0          \\
            0          & \delta^2/2 \\
            \delta     & 0          \\
            0          & \delta     \\
        \end{bmatrix}
    \]
    With $\delta$ time step of the simulation.
    The \textbf{B} input matrix change accordingly with the acceleration input (of what we suppose we know only the magnitude)
    \[
        B=\begin{Bmatrix}
            \begin{bmatrix}
                0 & 0 \\
                0          & 0 \\
                0     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                \delta^2/2 & 0 \\
                0          & 0 \\
                \delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                -\delta^2/2 & 0 \\
                0          & 0 \\
                -\delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & \delta^2/2 \\
                0 & 0          \\
                0 & \delta     \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & -\delta^2/2 \\
                0 & 0          \\
                0 & -\delta     \\
            \end{bmatrix}
        \end{Bmatrix}
    \]
    The \textbf{G} matrix is a merge between the "positive" matrices .

>>>>

\section*{Introduction}
\justify
The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
agent's tracking. The agent switches between linked models of movement by the means of a Markov chain. The goal is evaluate the best trade-off
between error on estimated position and real position and number of messagesses involved in the tracking.

@@

    The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep, and

@@

    between one sensor and the following one in any direction of the grid, as soon as the agent exceed the imposed maxiumum distance from the sensor,
    the device will stop sensing.

@@

    more power efficient and to avoid useless data stream towards sensors that aren't currently in range and sensing.

@@

    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure above.

@@

    The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 

@@

    Different state can receive and send different messagesses. A sensor in On state has the moving

@@

        z(k)=h(x(k))+v(k)

@@

    where $h(x)$ is the polar to cartesian cordinates transfor
    \begin{equation*}
        \begin{bmatrix}
            \rho\\ \alpha
        \end{bmatrix}=
    \end{equation*}

@@

            \frac{x}{(x^{2}+y^{2})^{1/2}} & \frac{y}{(x^{2}+y^{2})^{1/2}}& 0& 0 \\
            \frac{-y}{(x^{2}+y^{2})}  & \frac{x}{(x^{2}+y^{2})}& 0& 0 \\

@@

    \subsection*{Random walk and Unycicle model}
    The target in this simulation can move accordingly to two families of models, both are Markov processes.
    \\
    TABELLA CON DA UNA PARTE LE MODES DI UNO E DELL'ALTRO AL POSTO DI SPIEGARLO A PAROLE
    \\

    In the case of the random walk we choosen to have 5 states: costant velocity, positive or negative acceleration
    on x direction and positive or negative deceleration on y direction. The Transition matrix 
    associated with the Markov's chain is shown below
    \begin{equation*}
        \begin{bmatrix}
            0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
        \end{bmatrix}
    \end{equation*}
    The linear system describing the evolution of the state is 
    \begin{equation}
        x(k+1)= Ax(k) + B(s)u(k) + Gw(k)
    \end{equation}
    Where $x(k)$ is the state at the current timestep, $u(t)$ is the input and $w(k)$ is the process noise.
    In this case the state is a vector of the cartesian cordinates and their relative speed, while the input 
    is the acceleration which the noise will influence. 
    State,state and noise matrix associate to the random walk has shown below:
    \[ x=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
            1 & 0 & \delta & 0      \\
            0 & 1 & 0      & \delta \\
            0 & 0 & 1      & 0      \\
            0 & 0 & 0      & 1      \\
        \end{bmatrix}
        G=\begin{bmatrix}
            \delta^2/2 & 0          \\
            0          & \delta^2/2 \\
            \delta     & 0          \\
            0          & \delta     \\
        \end{bmatrix}
    \]
    With $\delta$ time step of the simulation.
    \\
    We hypothesize that the input is unknown in direction but known in magnitude. This set according to the current state at which the markov process is at the timestep.
    This is modeled though the switch between a set of matrices $B(s)$ that change according to the chain's state $s$.
    \[
        B(s)=\begin{Bmatrix}
            \begin{bmatrix}
                0 & 0 \\
                0          & 0 \\
                0     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                \delta^2/2 & 0 \\
                0          & 0 \\
                \delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                -\delta^2/2 & 0 \\
                0          & 0 \\
                -\delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & \delta^2/2 \\
                0 & 0          \\
                0 & \delta     \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & -\delta^2/2 \\
                0 & 0          \\
                0 & -\delta     \\
            \end{bmatrix}
        \end{Bmatrix}
    \]
    It can be noticed that the matrix $G$ is a merge between the second and the fourth matrices found in the set $B(s)$ as the noise will act
    randomly in direction and magnitude at every time-step.
